---
title: enviroCaR
author: Nikolai Gorte, Simon Schoemaker
framework: revealjs
revealjs: {theme: default, transition: default, trasition-speed: slow}
mode: selfcontained
highlighter : prettify
hitheme: desert
--- {background: titel.jpg}

## enviroCaR 
<br>
### Analysis of Car Trajectories 
#### provided by the enviroCar Project
Nikolai Gorte & Simon Schoemaker 

--- {background: titel.jpg}

## Agenda


* Introduction enviroCaR
* What can be done?
  * trajectories package
  * spacetime package
* Future work

--- {background: titel.jpg}

## EnviroCaR
* R package
* https://github.com/enviroCar/enviroCaR
* Basic functions to load and analyse measurements from the envirocar server

--- {background: titel.jpg}

## Import Single Track
```{r setup, echo=FALSE,error=FALSE,message=FALSE, results='asis'}
require(enviroCaR)
require(fuzzyMM)
require(map3d)
require(rgl)
require(knitr)
require(spacetime)
knit_hooks$set(rgl = hook_rgl)
```

```{r getTrack}
tracks <- importSingleTrack("https://envirocar.org/api/stable", "52af4fd3e4b0593cce13bfc7")

```

--- {background: titel.jpg}
## Track Structure
```{r strtrack}
str(tracks)
```

--- {background: titel.jpg}

## Trajectory Classes 
```{r getDef}
getClassDef("Track", trajectories)
```

--- {background: titel.jpg}
## Import Several Tracks
* By ID, bbox or time interval
```{r getTracks}
ids <- getTrackIDs("https://envirocar.org/api/stable", bbox(tracks))
trcol <- importEnviroCar("https://envirocar.org/api/stable", ids[4:6])
```

--- {background: titel.jpg}
## Trajectory Classes 
```{r getDef2}
getClassDef("Tracks", trajectories)
getClassDef("TracksCollection", trajectories)
```


--- {background: titel.jpg}
## Some Statistics
```{r sumtrack}
summary(tracks)
```


--- {background: titel.jpg}
## stplot
* Works only for TracksCollection
```{r stplot, fig.height = 6, fig.align = 'center'}
stplot(trcol, scales = list(draw=TRUE))
```

--- {background: titel.jpg}
## stplot with Attributes
```{r stplot2, fig.height = 6, fig.align = 'center'}
stplot(trcol, attr = "speed", lwd = 3, by = "IDs")
```


--- {background: titel.jpg}
## Aggregate Track
```{r aggregate}
agg_track <- aggregateTrack(tracks, phen="CO2", interval=26)
str(agg_track)
```

--- {background: titel.jpg}
## Generalize Track
```{r generalize,warning=FALSE}
track <- tracks[1]
gen_track <- generalize(track, distance = 500)
str(gen_track)
```


--- {background: titel.jpg}
## Map Matching

Map matching is the process of associating a sorted list of user 
or vehicle positions to the road network on a digital map.


--- {background: titel.jpg}
## Map Matching

```{r mm, message=FALSE,comment="", fig.height = 6, fig.align = 'center'}
par(bg = "white")
data <- track@data
track_sp <- track@sp
track_sp <- SpatialPointsDataFrame(track_sp, data, proj4string=proj4string(track_sp), bbox=bbox(track_sp))
matched_track <- mm(track_sp, plot = TRUE)
```

--- {background: titel.jpg}
## Map Matching

```{r mm2, message=FALSE,comment="", fig.align = 'center',fig.height=6}
par(bg = "white")
drn <- create_drn(bbox(track_sp))
plot(coordinates(track_sp)[1:20,], col="blue", pch=16)
lines(drn@sl)
points(coordinates(matched_track)[1:20,], col="red", pch=16)
```

--- {background: titel.jpg}
## 3D Plot

```{r 3dplot, rgl=TRUE, fig.align = 'center', fig.height = 6}
par3d("zoom" = 0.35)
spplot3d(track@sp, radius = 1, open3d = FALSE, type="skobbler")
```
```{r, echo=FALSE}
rgl.close()
```

--- {background: titel.jpg}
## 3D Plot with Attributes

```{r 3dplot2, rgl=TRUE, fig.align = 'center',fig.height = 6}
par3d("zoom" = 0.35)
spplot3d(track_sp, att="GPS.Speed", radius = 1, open3d = FALSE, type="skobbler")
```

--- {background: titel.jpg}
## Summary

* enviroCaR package
* Trajectory classes
* Plots, aggregation, generalization
* Map matching
* 3D plot

--- {background: titel.jpg}
## Outlook

* Solving issues with existing methods
* Custom track statistic functions
* Integrate map matching
* Improve visualization


